Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 schemes.tex
Some edits

Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
is to gradually increase the coding density as the \ac{dof}\footnote{We refer
as degrees of freedom to the dimension of the linear span from the coded
packets that a decoder has at a given point} increases, e.g. as the
cardinality of the set of \ac{l.i.} coded packets increases. This enables
\ac{TSNC} to significantly reduce the complexity particulary in the
beginning of the transmission process and also to control the decoding
delay. For \ac{TNSC}, we define the number of coded packets a
decoder needs to receive to decode a generation of $g$ packets. We call
this number the budget, $B$.

Provided a desired budget, $B \geq g$, and the decoders \ac{dof} it can be
estimated how sparse the coded packets should be to finish a transmission in
time.

>>>>

Therefore, in \ac{TSNC}, a simple procedure for controlling this probability
is to gradually increase the coding density as the \ac{dof}\footnote{We refer
as degrees of freedom to the dimension of the linear span from the coded
packets that a decoder has at a given point} increases, e.g. as the
cardinality of the set of \ac{l.i.} coded packets increases. This enables
\ac{TSNC} to significantly reduce the complexity, particularly in the
beginning of the transmission process and also to control the decoding
delay. For \ac{TSNC}, we define the budget, $B \geq g$, to be a target
number of coded packets a transmitter wants to send to a receiver
for decoding a generation of $g$ packets.

Provided a desired budget $B$ and the \ac{dof}s of the
decoder, an encoder can estimate the required coding density to not exceed
the required y the budget. ow sparse the coded packets should be to finish a transmission in
time.
